LAGOS lake depth

### 2020-02-18 README.Rmd
link to tables not appendix
link fix
link to data summary pdf
rm badges

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)]() [![Code DOI](https://zenodo.org/badge/123951266.svg)](https://zenodo.org/badge/latestdoi/123951266)

### Data (see [data/lagosus_depth.csv]())

@@

@@

Appendix: [manuscript/appendix.pdf](manuscript/figures.pdf)

>>>>

### Data (see [data/lagosus_depth.csv](data/lagosus_depth.csv))

@@

Data Summary: [manuscript/data.pdf](manuscript/data.pdf)

@@

Tables: [manuscript/tables.pdf](manuscript/tables.pdf)
